Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-24 paper.qmd
Update cyclestreets sentence

Transport systems dominated by heavy and powerful private cars are inefficient, dangerous, and unhealthy.
Cars are a major and growing source of greenhouse gas emissions causing climate change [@winkler2023], a leading cause of premature death and injury due to road traffic collisions [@globals2018] , and a cause of disease due to physical inactivity and air, noise and (from tyres) microplastic pollution [@mattsson2023] [@welch2023] [@cavallaro2024].
Transport is responsible for 23% of global greenhouse gas (GHG) emissions, 70% of which are from road transport.
Nearly half of these emissions (around 10% of global emissions) are from passenger cars [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles.
Services that are only accessible by car lock-in car dependency [@gray2001; @shergold2012; @motte-baumvol2010].

@@

CycleStreets' services can be used by anyone for free, but we commissioned a bespoke routing service for CRUSE, to enable:

>>>>

Transport systems dominated by heavy and powerful private cars are inefficient, dangerous, and unhealthy.
Cars are a major and growing source of greenhouse gas emissions causing climate change [@winkler2023], a leading cause of premature death and injury due to road traffic collisions [@globals2018] , and a cause of disease due to physical inactivity and air, noise and (from tyres) microplastic pollution [@mattsson2023] [@welch2023] [@cavallaro2024].
Transport is responsible for 23% of global greenhouse gas (GHG) emissions, 70% of which are from road transport, with passenger cars accounting for nearly half of transport emissions (around 10% of global emissions) [@jaramillo2022].
The transport system encourages, enables and in some cases enforces unsustainable lifestyles.
Services that are only accessible by car lock-in car dependency [@gray2001; @shergold2012; @motte-baumvol2010].

@@

While CycleStreets offers a free routing API, we commissioned a custom routing service to enable:

### 2024-03-24 paper.tex
Update cyclestreets sentence

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the underlying methods, including disaggregation of
origin-destination data, incorporation of additional trip purposes,
routing, scenarios generation, and development of an intuitive user
interface. Commissioned and used by Transport Infrastructure Ireland,
CRUSE provides estimates of current and potential future cycling levels
under `snapshot' scenarios to inform investment decisions. The publicly
available results at https://cruse.bike/ enable planners, engineers, and
other stakeholders to make more evidence-based decisions. CRUSE goes
beyond previous work by: modeling networks at high spatial resolution;
simulating multiple trip purposes (social, shopping, personal utility,
recreational, and cycle touring) in addition to using official
origin-destination data; and providing estimates of `quietness' (a proxy
for cyclist comfort) at the route segment level. Three network types ---
`Fastest', `Balanced', and `Quietest' --- help plan both arterial and
residential cycle networks. Workshops and unstructured interviews with
stakeholders show that the tool is already being used in practice to
inform urban, inter-urban, and rural network plans. The approach is
flexible and open-source, allowing the underlying ideas and code to be
adapted, supporting effective cycling policies and interventions
internationally.
\end{abstract}

>>>>

\begin{abstract}
This paper describes an approach for developing strategic cycle network
planning tools. Based on our experience developing and deploying the
Cycle Route Uptake and Scenario Estimation (CRUSE) Tool for Ireland, we
outline the underlying methods, including disaggregation of
origin-destination data, incorporation of additional trip purposes,
routing, scenario generation, and development of an intuitive user
interface. Commissioned and used by Transport Infrastructure Ireland,
CRUSE provides estimates of current and potential future cycling levels
under `snapshot' scenarios to inform investment decisions. The publicly
available results at https://cruse.bike/ enable planners, engineers, and
other stakeholders to make more evidence-based decisions. CRUSE goes
beyond previous work by: modeling networks at high spatial resolution;
simulating multiple trip purposes (social, shopping, personal utility,
recreational, and cycle touring) in addition to using official
origin-destination data; and providing estimates of `quietness' (a proxy
for cyclist comfort and route preference) at the route segment level.
Three network types --- `Fastest', `Balanced', and `Quietest' --- help
plan both arterial and residential cycle networks. Workshops and
unstructured interviews with stakeholders show that the tool is already
being used in practice to inform urban, inter-urban, and rural network
planning. The approach is flexible and open-source, allowing the
underlying ideas and code to be adapted, supporting effective cycling
policies and interventions internationally.
\end{abstract}
